Reanalysis Step 5: Outcome Analysis with Full Four-Treatment Interaction

### 2025-09-02 reanalysis-5-outcome_analysis-full_interaction.qmd
fix fix fix fix

# Check specific overlaps with focal laser
if (sum(first_data$focal_laser_flag) > 0) {
  focal_patients <- first_data[first_data$focal_laser_flag == 1, ]
  log_message(paste0("Total focal laser patients: ", nrow(focal_patients)))
  log_message(paste0("  Focal only: ", sum(focal_patients$n_treatments == 1)))
  log_message(paste0("  Focal + anti_VEGF: ", sum(focal_patients$anti_VEGF == 1)))
  log_message(paste0("  Focal + PRP: ", sum(focal_patients$PRP_flag == 1)))
  log_message(paste0("  Focal + other: ", sum(focal_patients$other_inject == 1)))
}

>>>>

# Check specific overlaps with focal laser
if (sum(as.numeric(as.character(first_data$focal_laser_flag))) > 0) {
  focal_patients <- first_data[as.numeric(as.character(first_data$focal_laser_flag)) == 1, ]
  log_message(paste0("Total focal laser patients: ", nrow(focal_patients)))
  log_message(paste0("  Focal only: ", sum(focal_patients$n_treatments == 1)))
  log_message(paste0("  Focal + anti_VEGF: ", sum(as.numeric(as.character(focal_patients$anti_VEGF)))))
  log_message(paste0("  Focal + PRP: ", sum(as.numeric(as.character(focal_patients$PRP_flag)))))
  log_message(paste0("  Focal + other: ", sum(as.numeric(as.character(focal_patients$other_inject)))))
}
